Tutorial_2b

### 2024-10-20 Tutorial_2b.Rmd
update stat_lineribbon 2b

  ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-40,-30,-20,-10,0,10,20,30,40), limits = c(-40,40)) +
  labs(x = "time bin", y = "logit-ca") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ factor(condition,levels=c("congruent trial 500","congruent trial 1000","congruent trial 1500","incongruent trial 500","incongruent trial 1000","incongruent trial 1500")))

>>>>

  ggplot(aes(x = period_9, y = value)) +
  stat_lineribbon(point_interval = mean_hdi,.width = c(0.5, 0.8, 0.95),show.legend=T) +
  scale_fill_brewer() +
  geom_hline(yintercept=0, linetype="dashed", color = "red") +
  scale_x_continuous(breaks = c(-3:6), labels=c(((-3:6)+9)*40),
                     limits = c(-3,6)) +
  scale_y_continuous(breaks = c(-50,-40,-30,-20,-10,0,10,20,30,40,50), limits = c(-50,50)) +
  labs(x = "time bin", y = "logit-ca") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90),
        panel.background = element_rect(fill="white", color="black"),
        legend.position = "top") +
  facet_wrap(~ factor(condition,levels=c("congruent trial 500","congruent trial 1000","congruent trial 1500","incongruent trial 500","incongruent trial 1000","incongruent trial 1500")))
